Title

### 2013-03-14 inc/gun/gun_model.tex
finished including andreas comments on extension chapter

In the acceleration region of a UEM column, a constant electric field is applied to the newly created electron pulse, increasing its velocity until it achieves its ultimate velocity just upon leaving the region at the anode aperture.
As seen in Section \ref{sec:const_force}, this constant electric field does not affect the intrapulse dynamics, however the electric field that nears this aperture turns outward, causing the anode itself to act as a negative transverse lens. %TODO reference
Additionally, the longitudinal electric field stregth sharply decreases near the anode.
Because the front of the pulse sees this change before the back, this changing field acts as a pulse compression element.

@@

To model an acceleration region, one must assume a form for the accelerating field.
From that form one may derive the terms governing the pulse dynamics. Initially, assume that the on-axis field is purely in the longitudinal direction, which may be thought of as an implication of radial symmetry.
Mathematically, that is
\begin{equation}
  \vec{F}(r^{\prime}=0,z^{\prime}) = F_z (0,z^{\prime}) \hat{z}
\end{equation}
where as before, the primed coordinates are the location of the center of the pulse.

To first model the longitudinal (compression) action at the anode %TODO ref
on electrons that are a distance $z$ ahead or behind of the center of the pulse feel a slightly different field, 
\begin{equation}
  F_z(0,z^{\prime} - z) \approx F_z(0,z^{\prime} - z) + \frac{\partial F_z}{\partial z^{\prime}} z
\end{equation}
Again, the constant leading term does not contribute to the intrapulse dynamic, however the second term is of the proper form to say that in this region the anode's longitudinal compression strength $M_z$ is given by
\begin{equation}
  M_z = \frac{\partial F_z}{\partial z^{\prime}} \, \text{.}
\end{equation}

@@

We may choose to assume that the on-axis field is defined as a smoothed step down function
\begin{equation} \label{eq:anode_tanh}
  F_z(0,z^{\prime}) = \frac{qV}{2z^{\prime}_A} \left( 1 - \tanh \left( \frac{ z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \right)
\end{equation}
where $V$ is the accelerating potential, $z^{\prime}_A$ is the position of the anode (the cathode assumed to be at $z^{\prime} = 0$) and $s$ is a constant quantifying the ``sharpness'' of the fall-off of the electric field.
Indeed, this form is analgous to the super-Gaussian envalope (\ref{eq:reg_of_influence}), however it is open ended on the cathode side, which is necessary for the electrons to be accelerated away from the photocathode.
Given this form (demonstrated in Section \ref{sec:gun_design}) the ``lensing'' strengths are then
\begin{gather}
  M_{\smallT} = -\frac{qVs}{4z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \\
  M_z = \frac{qVs}{2z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \, \text{.}
\end{gather}
As with the RF cavity, remember to include the on-axis force (\ref{eq:anode_tanh}) in the overall pulse propagation.

\begin{figure}
  \centerline{
    \subfloat[][]{
      \label{fig:field_on_axis}
      \input{onaxis}
    }
    \subfloat[][]{
      \label{fig:tanh_sharpness}
      \input{sharpness}
    }
  }
  \caption[An example of a tahn form acceleration region for three different ``sharpness'' values]{
    An example of a tahn form acceleration region (overall length 6.35mm) for three different ``sharpness'' values.
    The square data points in \protect\subref{fig:field_on_axis} represent the on-axis electric field data from FEM simulations, see Section \ref{sec:gun_design}.
    The colored electric fields in \protect\subref{fig:field_on_axis} correspond to the pulse width (solid) and length (dashed) in \protect\subref{fig:tanh_sharpness}.
  }
  \label{fig:gun-sharpness}
\end{figure}

\ref{fig:gun-sharpness} shows an example acceleration region for three values of the ``sharpness'' $s$.
What is clear from this figure is that the dynamics are not highly coupled to the value of this hard-to-quantify parameter.
For all values of $s$ the divergence of the beam is equal (thought the size may vary slightly).
Interestingly the length of the pulse is stabilized on exiting the anode, coming very nearly to a constant length (not expanding nor contracting).
This effect is due to the slower electrons remaining in the cavity longer and thus receiving an additional kick, as described in \cite{oudheusden_electron_2007}.

>>>>

In the acceleration region of a UEM column, a constant electric field is applied to the newly created electron pulse, increasing its velocity until it achieves its ultimate velocity just upon leaving the region at the anode aperture.
As seen in Section \ref{sec:const_force}, this constant electric field does not affect the intrapulse dynamics, however the distortion in the electric field near this aperture causes the anode itself to act as a negative transverse lens. %TODO reference
Additionally, the longitudinal electric field stregth sharply decreases near the anode.
As the front of the pulse sees this change before the back, this changing field also acts as a pulse compression element.

@@

To model an acceleration region, one must assume a form for the accelerating field.
From that form one may derive the terms governing the pulse dynamics. Initially, assume that the on-axis field is purely in the longitudinal direction, which may be thought of as an implication of radial symmetry.
Mathematically, that is
\begin{equation}
  \vec{F}(r^{\prime}=0,z^{\prime}) = F_z (0,z^{\prime}) \hat{z} = e E_z (0,z^{\prime}) \hat{z}
\end{equation}
where as before, the primed coordinates are the location of the center of the pulse.

To first model the longitudinal (compression) action at the anode, %TODO ref
consider electrons that are a distance $z$ ahead or behind of the center of the pulse and so feel a slightly different force, 
\begin{equation}
  F_z(0,z^{\prime} - z) \approx F_z(0,z^{\prime} - z) + \frac{\partial F_z}{\partial z^{\prime}} z
\end{equation}
Again, the constant leading term does not contribute to the intrapulse dynamic, however the second term is of the proper form to say that in this region the anode's longitudinal compression strength $M_z$ is given by
\begin{equation}
  M_z = \frac{\partial F_z}{\partial z^{\prime}} = e \frac{\partial E_z}{\partial z^{\prime}} \, \text{.}
\end{equation}

@@

We may choose to assume that the on-axis field is defined as a smoothed step down function
\begin{equation} \label{eq:anode_tanh}
  F_z(0,z^{\prime}) = \frac{eV}{2z^{\prime}_A} \left( 1 - \tanh \left( \frac{ z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \right)
\end{equation}
where $V$ is the accelerating potential, $z^{\prime}_A$ is the position of the anode (the cathode assumed to be at $z^{\prime} = 0$) and $s$ is a constant quantifying the ``sharpness'' of the fall-off of the electric field.
Indeed, this form is analgous to the super-Gaussian envalope (\ref{eq:reg_of_influence}), however it is open ended on the cathode side, which is necessary for the electrons to be accelerated away from the photocathode.
Given this form (demonstrated in Section \ref{sec:gun_design}) the ``lensing'' strengths are then
\begin{gather}
  M_{\smallT} = -\frac{eVs}{4z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \\
  M_z = \frac{eVs}{2z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \, \text{.}
\end{gather}
As with the RF cavity, one needs to include the on-axis force (\ref{eq:anode_tanh}) in the overall pulse propagation kinematics.

\begin{figure}
  \centerline{
    \subfloat[][]{
      \label{fig:field_on_axis}
      \input{onaxis}
    }
    \subfloat[][]{
      \label{fig:tanh_sharpness}
      \input{sharpness}
    }
  }
  \caption[An example of a tanh form acceleration region for three different ``sharpness'' values]{
    An example of a tahn form acceleration region (overall length 6.35mm) for three different ``sharpness'' values.
    The square data points in \protect\subref{fig:field_on_axis} represent the on-axis electric field data from FEM simulations, see Section \ref{sec:gun_design}.
    The colored electric fields in figure \protect\subref{fig:field_on_axis} correspond to the pulse width (solid) and length (dashed) in figure \protect\subref{fig:tanh_sharpness}.
  }
  \label{fig:gun-sharpness}
\end{figure}

\ref{fig:gun-sharpness} shows an example acceleration region for three values of the ``sharpness'' $s$ as well as longitudinal FEM field data which is explained further in Section \ref{sec:gun_design}.
%TODO possibly remove the FEM data? it doesn't help much here and is confusing since it hasn't been introduced
What is clear from this figure is that the dynamics are not highly coupled to the value of this hard-to-quantify parameter.
For all values of $s$ the divergence of the beam is equal (though the size may vary slightly).
Interestingly the length of the pulse is stabilized on exiting the anode, coming very nearly to a constant length (not expanding nor contracting).
This effect is due to the slower electrons remaining in the cavity longer and thus receiving an additional kick, as described in \cite{oudheusden_electron_2007}.
